### 2019-02-26 intro.tex
minor

Using the serverless model, application developers upload 
arbitrary computations in high level languages
as stateless functions to cloud-hosted, serverless platforms.
Functions are invoked (i.e. triggered)
automatically by the cloud in response to updates to other cloud services
(e.g. storage, queues, notification services, and API gateways, among others), which 
the developer configures. Serverless functions
communicate, persist, and access data only 
through their inputs or via shared, storage services.  
As a result, serverless applications are inherently elastic and can 
implement highly concurrent and parallel tasks.
In public clouds, users pay a small fee for the resources their 
functions use during execution, resulting in very low cost cloud use.
Although now available from all public cloud providers and as open 
source for private cloud systems, 
Amazon Web Services (AWS) Lambda\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf}} %~\cite{ref:awslambdadg} 
was the first and is the most widely used
serverless public cloud platform.
%awslambda: https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf

>>>>

Using the serverless model, application developers upload 
arbitrary computations in high level languages
as stateless functions to cloud-hosted, serverless platforms.
Functions are invoked (i.e. triggered)
automatically by the cloud in response to updates to other cloud services
(e.g. storage, queues, notification services, and API gateways, 
among others), which 
the developer configures. Serverless functions must execute in under
a time bound (e.g. 15 minutes) and use less than a maximum memory size 
(e.g. 3GB) or else the platform will terminate the function.
communicate, persist, and access data only 
through their inputs or via shared, storage services.  
As a result, serverless applications are inherently elastic and can 
implement highly concurrent and parallel tasks.
In public clouds, users pay a small fee for the resources their 
functions use during execution, resulting in very low cost cloud use.
Although now available from all public cloud providers and as open 
source for private cloud systems, 
Amazon Web Services (AWS) Lambda\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf}} %~\cite{ref:awslambdadg} 
was the first and is the most widely used
serverless public cloud platform.
%awslambda: https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf

### 2019-02-26 results.tex
minor

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we have verified the optimized allocated memory allows all hyperparameter settings run successfully.

>>>>

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we 
have verified that the optimized allocated memory allows all 
hyperparameter settings complete successfully.
